DOM Review Summary

### 2024-03-18 Analysis/ReviewSummary/ReviewSummary.qmd
Number of sites fig
Number of sites figure, adjusted min/max/median text

dataCollection_clean <- review_DataCollection |>
  filter(Status == "Complete") |>
  mutate(Duration = as.numeric(Duration)) |>
  separate_wider_delim(cols = Primary_Occasions, 
                       delim = "-",
                       names = c("Primary_Min", "Primary_Max"),
                       too_few = "align_start") |>
  separate_wider_delim(cols = Secondary_Occasions, 
                       delim = "-",
                       names = c("Secondary_Min", "Secondary_Max"),
                       too_few = "align_start") |>
  separate_wider_delim(cols = Site_Number, 
                       delim = "-",
                       names = c("SiteNumber_Min", "SiteNumber_Max"),
                       too_few = "align_start") |>
  mutate(Primary_Max = if_else(is.na(Primary_Max),
                               Primary_Min, Primary_Max),
         Secondary_Max = if_else(is.na(Secondary_Max),
                                 Secondary_Min, Secondary_Max),
         SiteNumber_Max = if_else(is.na(SiteNumber_Max),
                                  SiteNumber_Min, SiteNumber_Max)) |>
  mutate(across(c(Primary_Min, Primary_Max, 
                  Secondary_Min, Secondary_Max,
                  SiteNumber_Min, SiteNumber_Max),
                as.numeric))
```

@@

Study duration, defined as the length of time between the first and last survey, ranged from **`{r} min(dataCollection_clean$Duration)`** month to **`{r} max(dataCollection_clean$Duration)/12`** years.

@@

@@

@@

>>>>

dataCollection_clean <- review_DataCollection |>
  filter(Status == "Complete") |>
  mutate(ID_clean = str_extract(ID, "[:digit:]+")) |>
  mutate(Duration = as.numeric(Duration)) |>
  separate_wider_delim(cols = Primary_Occasions, 
                       delim = "-",
                       names = c("Primary_Min", "Primary_Max"),
                       too_few = "align_start") |>
  separate_wider_delim(cols = Secondary_Occasions, 
                       delim = "-",
                       names = c("Secondary_Min", "Secondary_Max"),
                       too_few = "align_start") |>
  separate_wider_delim(cols = Site_Number, 
                       delim = "-",
                       names = c("SiteNumber_Min", "SiteNumber_Max"),
                       too_few = "align_start") |>
  mutate(Primary_Max = if_else(is.na(Primary_Max),
                               Primary_Min, Primary_Max),
         Secondary_Max = if_else(is.na(Secondary_Max),
                                 Secondary_Min, Secondary_Max),
         SiteNumber_Max = if_else(is.na(SiteNumber_Max),
                                  SiteNumber_Min, SiteNumber_Max)) |>
  mutate(across(c(Primary_Min, Primary_Max, 
                  Secondary_Min, Secondary_Max,
                  SiteNumber_Min, SiteNumber_Max),
                as.numeric))
```

@@

Study duration, defined as the length of time between the first and last survey, ranged from **`{r} min(dataCollection_clean$Duration)`** month to **`{r} max(dataCollection_clean$Duration)/12`** years, with a median of **`{r} median(dataCollection_clean$Duration`** months.

@@

The number of sampling occasions varied considerably. The number of primary occasions ranged from just **`{r} min(dataCollection_clean$Primary_Max)`** to **`{r} max(dataCollection_clean$Primary_Max)`** with a median of **`{r} median(dataCollection_clean$Primary_Max)`**.

The number of secondary occasions from **`{r} min(dataCollection_clean$Secondary_Max, na.rm = TRUE)`** to **`{r} max(dataCollection_clean$Secondary_Max, na.rm = TRUE)`** with a median of **`{r} median(dataCollection_clean$Secondary_Max, na.rm = TRUE)`**.

@@

The most common method for recording detections was human surveys, either structured (e.g. time-bound point counts or transects) or unstructured (searches of sites). Autonomous detection methods (camera traps & acoustic monitors) were used infrequently, despite their potential suitability.

```{r DataCollection_SamplingMethod}
#| echo: false

dataCollection_clean |>
  mutate(Total = length(unique(ID_clean))) |>
  separate_rows(Detection_Method, sep = ", ") |>
  summarise(Articles = n(), 
            #Proportion = round(Articles/Total, 2),
            .by = c(Detection_Method, Total)) |>
  mutate(Percentage = round(Articles/Total, 2)*100) |>
  select(Detection_Method, Articles, Percentage) |>
  filter(!Detection_Method %in% c("66", NA, "Unspecificed",
                                  "Survey", "Incidental")) |>
  arrange(Percentage) |>
  mutate(Detection_Method = case_when(Detection_Method == "AudioVisual" ~ "Human structured survey",
                                      Detection_Method == "Search" ~ "Human unstructured search",
                                      Detection_Method == "Trapping" ~ "Physical trapping",
                                      Detection_Method == "Camera" ~ "Camera trapping",
                                      Detection_Method == "Citizen" ~ "Citizen science",
                                      Detection_Method == "Bioacoustic" ~ "Acoustic monitor")) |>
  mutate(Detection_Method = fct_inorder(Detection_Method)) |>

  ggplot() +
  geom_col(aes(x = Percentage, y = Detection_Method), fill = "darkslategrey") +
  labs(title = "Detection method",
       subtitle = "Multiple methods per article permitted",
       x = "Percentage of articles", y = "") +
  xlim(c(0,50))
```

## Number of sites

The number of sites where surveys were conducted ranged widely from **`{r} min(dataCollection_clean$SiteNumber_Max, na.rm = TRUE)`** to **`{r} max(dataCollection_clean$SiteNumber_Max, na.rm = TRUE)`**, with a median site count of **`{r} median(dataCollection_clean$SiteNumber_Max, na.rm = TRUE)`**.

```{r DataCollection_numberSites}
#| echo: false

dataCollection_clean |>
  filter(!is.na(SiteNumber_Max)) |>

  ggplot() +
  geom_histogram(aes(x = SiteNumber_Max), 
                 binwidth = 0.1, 
                 fill = "darkslategrey") +
  scale_x_continuous(transform = "log10",
                     breaks = c(5, 10, 25, 50, 100, 500, 1000, 10000)) +
  labs(title = "Number of sites",
       x = "Number of sites", y = "Number of articles")
```

@@

```{r DataCollection_Sampling}
